\documentclass[onecolumn, draftclsnofoot,10pt, compsoc]{IEEEtran}
\usepackage{graphicx}
\usepackage{url}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{array, longtable}
\usepackage{listings}%
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\lstset{%
  basicstyle=\ttfamily\footnotesize,
  backgroundcolor=\color{gray!10},%
  tabsize=3,
  language=bash,
  columns=fullflexible,
  %frame=shadowbox,
  frame=leftline,
  rulesepcolor=\color{gray},
  xleftmargin=20pt,
  framexleftmargin=15pt,
  keywordstyle=\color{black}\bf,
  commentstyle=\color{OliveGreen},
  %stringstyle=\color{red},
  breaklines=true,
  %numbers=left,
  %numberstyle=\tiny,
  %numbersep=5pt,
  showstringspaces=false,
  postbreak=\mbox{{/}\space},
  emph={str},emphstyle={\color{magenta}},
  alsoletter=-,%to allow qemu-system...
  %add extra keywords here.
  emph={%  
    cd, ls, cp, qemu-system-i386, mv, mkdir, make, for, git, gdb, uname, tar, modprobe, echo, cat, sync, dd, dmesg, diff, chmod%
    },emphstyle={\color{black}\bf},
  %remove keywords below
  deletekeywords={if, enable, continue}
}%


\usepackage{geometry}
\geometry{textheight=9.5in, textwidth=7in}

\usepackage{graphicx}
\graphicspath{{images/}}

% 1. Fill in these details
\def \TeamName{		Group 20}
\def \GroupMemberOne{			Max Moulds}
\def \GroupMemberTwo{			Monica Sek}
\def \GroupMemberThree{			Nicholas Wong}
\def \ProfessorPerson{		Dr. Kevin McGrath}


% 2. Uncomment the appropriate line below so that the document type works
\def \DocType{		HW3 Writeup
				}

\newcommand{\NameSigPair}[1]{\par
\makebox[2.75in][r]{#1} \hfil 	\makebox[3.25in]{\makebox[2.25in]{\hrulefill} \hfill		\makebox[.75in]{\hrulefill}}
\par\vspace{-12pt} \textit{\tiny\noindent
\makebox[2.75in]{} \hfil		\makebox[3.25in]{\makebox[2.25in][r]{Signature} \hfill	\makebox[.75in][r]{Date}}}}
% 3. If the document is not to be signed, uncomment the RENEWcommand below
%\renewcommand{\NameSigPair}[1]{#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{titlepage}
    \pagenumbering{gobble}
    \begin{singlespace}
        \hfill
        \par\vspace{.2in}
        \centering
        \scshape{
            \huge Operating Systems II \DocType \par
            {\large\today}\par
            \vspace{.5in}
            \vfill
            \vspace{5pt}
            %{\Large\NameSigPair{\ProfessorPerson}\par}
						{\large Prepared for }\par
						\ProfessorPerson\par
            {\large Prepared by }\par
            \GroupMemberOne\par
						\GroupMemberTwo\par
						\GroupMemberThree\par
            \vspace{5pt}
            \vspace{20pt}
        }
        \begin{abstract}
        %6. Fill in your abstract
       		This document is the writeup for homework 3 of Operating Systems II Spring term 2018, written by Group 20.
					\end{abstract}
    \end{singlespace}
\end{titlepage}
\newpage
\pagenumbering{arabic}
\tableofcontents
% 7. uncomment this (if applicable). Consider adding a page break.
%\listoffigures
%\listoftables
\clearpage

\section{Design Plan}
For this assignment we were tasked with writing a RAM Disk device driver for the Linux Kernel which should allocate a chunk of memory and present it as a block device. This requires the use of the Linux Kernel's Crypto API to add encryption to the created block device such that the device driver encrypts and decrypts data when it is written and read.

Having created a filesystem in memory before we began from that shared knowledge by researching the difference between what was done before and what is being asked in this assignment \cite{jamescoyle}. Using the logical progression from creating an unecrypted block device residing entirely in memory first and then testing to then adding a level of encryption to that device. The last element, encryption, is where the majority of the work and research was needed. 

We used the example block device given in the assignment description and extended encryption to operations that use that device. We included the crypto header, set a 16 digit base secret key and compiled our block device a module in a similar manner to assignment 2. 

Next we had to implement a cipher at a low level. In the simple block device code when a write or read was required we changed the unencrypted function logic to support our encryption scheme using the crypto api. This created a transformation of the data being written or read. We used a call to the crypto library function crypto\textunderscore cipher\textunderscore encrypt\textunderscore one for writes crypto\textunderscore cipher\textunderscore decrypt\textunderscore one for reads. 

This was built out and tested using printk statements to check the changes in situ. Further explanation of the testing and verification processes used is described in the following sections. 


%\newpage

\section{Version Control Log}

%% uncomment this when you have the file on machine
%%\input{gitlog.tex}

%%manually pasted generated table for viewing on sharelatex, remove later
\begin{longtable} {|l|l|p{13cm}|}
    \hline
    \textbf{Author} & \textbf{Date} & \textbf{Message} \\ \hline
nickywongdong & 2018-05-23 & uploading assignment description \\ \hline
nickywongdong & 2018-05-23 & downloading clean linux image \\ \hline
nickywongdong & 2018-05-23 & uploading initial related files \\ \hline
nickywongdong & 2018-05-23 & updating readme unordered list \\ \hline
nickywongdong & 2018-05-23 & updating ordered sublist items \\ \hline
nickywongdong & 2018-05-23 & updating readme again \\ \hline
nickywongdong & 2018-05-23 & once again updating readme \\ \hline
nickywongdong & 2018-05-23 & adding initial simple block device from example online source \\ \hline
nickywongdong & 2018-05-23 & testing initial simple block device without adding crypto \\ \hline
nickywongdong & 2018-05-23 & adding crypto parts to encrypt/decrypt data \\ \hline
nickywongdong & 2018-05-23 & testing some more crypto gegeneration \\ \hline
nickywongdong & 2018-05-24 & adding specific qemu command used for easy access \\ \hline
nickywongdong & 2018-05-24 & updating sbd to one hopefully compatible with kernel \\ \hline
nickywongdong & 2018-05-24 & testing with same crypto from last version of sbd.c \\ \hline
nickywongdong & 2018-05-24 & adding req->buffer to use bio\_data() found in swim.c -- Must be update for kernel version \\ \hline
nickywongdong & 2018-05-24 & successful compilation, plan to run with qemu to test later \\ \hline
nickywongdong & 2018-05-24 & updating printk statements for correctness \\ \hline
nickywongdong & 2018-05-24 & changing module author, and running ac1\_open script for linux kernel, and hw3 directory for teammates \\ \hline
nickywongdong & 2018-05-24 & adding command used for scp, and organized previous commands \\ \hline
nickywongdong & 2018-05-24 & adding commands used within qemu vitual machine to test kernel module \\ \hline
nickywongdong & 2018-05-25 & adding patch file \\ \hline
nickywongdong & 2018-05-25 & updating patch \\ \hline
nickywongdong & 2018-05-25 & adding block device in Kconfig \\ \hline
nickywongdong & 2018-05-25 & updating patch \\ \hline
nickywongdong & 2018-05-25 & updating patch \\ \hline
nickywongdong & 2018-05-25 & finalizing \\ \hline

\end{longtable}


\section{Work Log}
\begin{tabular}{|l|l|}
\hline
     May 23 & Began assignment by researching from the assignment description, and pulling examples from online sources\\\hline
     May 24 & Began development of crypto portion of the assigment\\\hline
     May 25 & Finalizing assignment with patch file\\\hline
     May 27 & Write up and review \\ \hline

\end{tabular}

\newpage

\section{Additional Questions}
\begin{enumerate}
    \item What do you think the main point of the assignment is?
    
     \begin{singlespace}
     In the context of operating systems and the components that provide upper level functionality this assignment requires familiarization with Linux block devices and crypto apis within a kernel. Within the context of development of a low level system component this assignment teaches one to deal with external documentation and using other external libraries to create a set of required functionalities. In the context of software development this is useful because it teaches one to develop in a way that others can use it. While this last point may be a stretch it is undoubtedly important if one plans to develop software used by others. 
 
    \end{singlespace}
    
    \item How did you personally approach the problem? Design the decisions, algorithm, etc.
    \begin{singlespace} 
    As mentioned previously the assignment was approached by building off previous knowledge gained from both previous assignments and experience outside of the class. We also relied on advice from the professor and from discussion with others familiar with the assignment goals. 

    
    \end{singlespace}
    
    \item How did you ensure your solution was correct? Testing details, for instance.
    \begin{singlespace} 
    To ensure correctness of our solution, we first made sure that the module was compiled and the .ko file existed after the make command.
    This file should be located in driver/block/ directory within the Yocto root directory.
    We then started up the virtual machine with the command similar to the one in the previous assignment, but this time removing the flag -net:none.
    This will allow us to scp the .ko file from our engr group directory into localhost.
    We then loaded the mod with insmod. The block device then showed up under the /dev directory and it was capable of being mounted to the system with mkfs.ext2.
    This caused the initialization to run within the module and demonstrate writing/reading with an additional crypto encryption/encryption process.

 
    \end{singlespace}
    
    \item What did you learn?
    \begin{singlespace} 
    While continuing to cement our understanding and comfort with developing Yocto kernel components and procedures we extended our general understanding of low level system components and their interaction with other kernel subsystems. This is most evident in the interaction between the kernel module we implemented to provide the block device and the corresponding functions used within that code that in turn used the already existing API to provide our needed cryptographic functionality.
    
    Implementation alone continued lessons begun in past assignments, this assignment brought about another element that forced us to learn. Testing and verifying our solution was not as straightforward as using the implemented changes and inspecting the output and led to greater understanding of development. Sometimes verification of a solution is tougher processes than the finding the initial solution itself. Additionally, cryptography has a higher degree of required verification since ramifications from a failure in a cryptographic implementation carry different ramifications from those in the past two assignments which mainly impact system performance relating to physical device such as a hard drive and the physical or operational damages from improper implementation. The impacts from improperly verified cryptographic functionality is complete loss of the functionality and intended service. That is a crytpographic integrity is either complete or non-existant whereas a poorly implemented seek algorithm for a hard drive device can still provide some level of service. 


    \end{singlespace}
    \item How should the TA evaluate your work? Provide detailed steps to prove correctness
    \begin{singlespace}
    Start with the 3.19.2 Yocto kernel source and our project submission and enter into that submission directory. Use the patch file given with this write up or located at 
    \end{singlespace}
    \begin{lstlisting}
    https://github.com/nickywongdong/CS444_GROUP20/blob/master/hw3/patch/hw3.patchc file in the block directory within the Yocto source.
    \end{lstlisting}
    \subsection*{Applying the patch and compiling the kernel image}
    \begin{singlespace}
    First, please apply the patch supplied to the v3.19.2 branch of the Yocto Kernel, and while in that directory check that patch applied by looking for the simple device block driver.

    Once compilation has completed, there should be a kernel image file in the x86 directory and subdirectory boot. Please start the VM using the following command changed to reflect booting from that image:
    \end{singlespace}
    \begin{lstlisting}
    > qemu-system-i386 -gdb tcp::5520 -S -nographic -kernel linux-yocto-3.19.2/arch/x86/boot/bzImage -drive file=core-image-lsb-sdk-qemux86.ext4,if=virtio -enable-kvm -usb -localtime --no-reboot --append "root=/dev/vda rw console=ttyS0 debug"

    \end{lstlisting}
    \begin{singlespace}
    Note that if the filesytem container {\bf core-image-lsb-sdk-qemux86.ext4} is not located in the parent directory of the Yocto kernel, change either the command to reference the filesystem container file or move that file to the parent directory. 
    \end{singlespace}
    
    And that concludes our writeup for HW3. Thank you. 
  
\end{enumerate}


\section{References}
\bibliographystyle{IEEEtran}  
\bibliography{CS444_project3_20}

\end{document}
